---
title: "Process various data lists"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

By **Christian McDonald**, Assistant Professor of Practice\
School of Journalism, Moody College of Communication\
University of Texas at Austin

This THCIC analysis will need various lists of columns and ICD-10 codes. This notebook defines them and write them to rds where they can be use in later analysis.

Of note, to turn a single-column rds import into a vector, use the following:

```txt
new_list <- read_rds("procedures-lists/filename.rds") %>% .$col_name_from_df
```

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
```

## THCIC column lists

The diagnostic and surgical procedure columns from the THCIC data are frequently used in `case_when()` statements and other vectors. This writes them to csv and rds for use later. I use my test data as a base point to find the columns.

There is an example data dictionary in the `resources` directory of this repo, or avialable online labeled as [User Manual, 2019](https://www.dshs.texas.gov/thcic/hospitals/Inpatientpudf.shtm).

### Import test data for column generation

```{r data_test}
testdata <- read_rds("data-test/ahrq_del_all_loop_test.rds")
```

### Diagnostic columns

Values are all the names of diagnostics columns from the data in a singe tibble with column named `diag`. 

```{r cols_diag}
cols_diag <- testdata %>% 
  select(contains("_DIAG"), -starts_with("POA")) %>%
  names() %>% 
  tibble::enframe(name = NULL) %>% 
  rename(diag = value)

cols_diag %>% 
  write_csv("procedures-lists/cols_diag.csv")

cols_diag %>% 
  write_rds("procedures-lists/cols_diag.rds")
  
```

### Surgical procedure columns

Values are all the names of surgical procedure columns from the data in a singe tibble with column named `surg`.

```{r cols_surg}
cols_surg <- testdata %>% 
  select(contains("SURG_PROC_CODE")) %>%
  names() %>% 
  tibble::enframe(name = NULL) %>% 
  rename(surg = value)

cols_surg %>% 
  write_csv("procedures-lists/cols_surg.csv")

cols_surg %>% 
  write_rds("procedures-lists/cols_surg.rds")
```

## AHRQ lists

These can come from IQI 33 or IQI 21. Some are in both. In addition to the links below they available in the `resources` directory of this repo.

- [IQI 33 Primary Cesarean Delivery Rate, Uncomplicated](https://qualityindicators.ahrq.gov/Downloads/Modules/IQI/V2019/TechSpecs/IQI_33_Primary_Cesarean_Delivery_Rate_Uncomplicated.pdf)
- [IQI 21 Cesarean Delivery Rate, Uncomplicated](https://qualityindicators.ahrq.gov/Downloads/Modules/IQI/V2019/TechSpecs/IQI_21_Cesarean_Delivery_Rate_Uncomplicated.pdf)

### All deliveries (DELOCMD)

All deliveries, identified by any-listed ICD-10-CM diagnosis code for outcome of delivery (DELOCMD). In both IQI 33 or IQI 21.

```{r delocmd}
delocmd_list <- c(
  "Z370",
  "Z371",
  "Z372",
  "Z373",
  "Z374",
  "Z3750",
  "Z3751",
  "Z3752",
  "Z3753",
  "Z3754",
  "Z3759",
  "Z3760",
  "Z3761",
  "Z3762",
  "Z3763",
  "Z3764",
  "Z3769",
  "Z377",
  "Z379"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(delocmd = value)

delocmd_list %>% 
  write_rds("procedures-lists/ahrq_delocmd.rds")

delocmd_list %>% nrow()
```

### Abnormal presentations (PRCSECD)

We first need the list of PRCSECD codes from `resources/IQI_Appendix_A_2019.pdf`: "Abnormal presentation, fetal death and multiple gestation diagnosis codes: (PRCSECD)."

The list of codes was extracted from the PDF and cleaned in OpenRefine to get the full list. The OpenRefine project is available in the `procedures/iqi-appendex-a` folder.

```{r prcsecd}
prcsecd_list <- read_csv("procedures-lists/IQI_Appendix_A.csv") %>% rename(prcsecd = codes)

prcsecd_list %>% 
  write_rds("procedures-lists/ahrq_prcsecd.rds")

prcsecd_list %>% nrow()
```

### Cesarean delivery MS-DRG codes: (PRCSE2G)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated. Also in IQI 21 Cesarean Delivery Rate, Uncomplicated.

```{r prcse2g}
# MS-DRG codes for Cesarean delivery (PRCSE2G*)
prcse2g_list <- c(
  "765",
  "766"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prcse2g = value)

prcse2g_list %>% 
  write_rds("procedures-lists/ahrq_prcse2g.rds")

prcse2g_list %>% nrow()
```

### Cesarean delivery updated

I found zero Cesarean births listed for 2019, so research found this article on [New DRG codes for C-sections and vaginal deliveries](https://www.mhswi.com/newsroom/New-DRG-codes-for-C-sections-and-vaginal-deliveries.html) and [this post](http://bok.ahima.org/doc?oid=302634#.XlK88JNKg6g), which indicate changes in billing codes for 2019. Here I extend the existing PRCSE2G list to add these new codes, calling it prcse2g_v2_list

```{r prcse2g_v2}
prcse2g_v2_list <- c(
  "765",
  "766",
  "783",
  "784",
  "785",
  "786",
  "787",
  "788"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prcse2g = value)

prcse2g_v2_list %>% 
  write_rds("procedures-lists/ahrq_prcse2g_v2.rds")

prcse2g_v2_list %>% nrow()
```

### Hysterotomy procedure codes: (PRCSE2P)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated. Also in IQI 21 Cesarean Delivery Rate, Uncomplicated.

```{r prcse2p}
prcse2p_list <- c(
  "10A00ZZ",
  "10A03ZZ",
  "10A04ZZ"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prcse2p = value)

prcse2p_list %>% 
  write_rds("procedures-lists/ahrq_prcse2p.rds")

prcse2p_list %>% nrow()
```

### Cesarean delivery procedure codes: (PRCSECP)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated. Also in IQI 21 Cesarean Delivery Rate, Uncomplicated.

```{r prcsecp}
prcsecp_list <- c(
  "10D00Z0",
  "10D00Z1",
  "10D00Z2"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prcsecp = value)

prcsecp_list %>% 
  write_rds("procedures-lists/ahrq_prcsecp.rds")

prcsecp_list %>% nrow()
```

### Previous Cesarean delivery diagnosis codes: (PRVBACD)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated

- with any-listed ICD-10-CM diagnosis codes for previous Cesarean delivery (PRVBACD*)

```{r prvbacd}
prvbacd_list <- c(
  "O3421",
  "O34211",
  "O34212",
  "O34219",
  "O6641"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prvbacd = value)

prvbacd_list %>% 
  write_rds("procedures-lists/ahrq_prvbacd.rds")

prvbacd_list %>% nrow()
```

## Other lists used

### Child-bearing age codes

Researchers at the Office of Health Affairs-Population Health, The University of Texas System work with the THCIC file daily and they suggest filtering deliveries to women of normal child-bearing age, 15-49.

The codes for the ages 15-49 include 05-12. For HIV or drug patients it includes 23 (18-44 yrs).

```{r age}
age_list <- c(
  "05",
  "06",
  "07",
  "08",
  "09",
  "10",
  "11",
  "12",
  "23"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(age = value)

age_list %>% 
  write_rds("procedures-lists/utoha_age.rds")

age_list %>% nrow()

```

## Leapfrog Episiotomy lists

These definitions come from [Leapfrog Hospital survey measure specifications](https://www.leapfroggroup.org/sites/default/files/Files/2019HospitalSurvey_20190529_v8.0%20%28version%203%29.pdf). There is also a copy in the `resources` directory of this repo.

### Vaginal MS_DRG codes

```{r vag_msdrg}
vag_msdrg_list <- c(
  "767",
  "768",
  "774",
  "775",
  "796",
  "797",
  "798",
  "805",
  "806",
  "807"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(vag_msdrg = value)

vag_msdrg_list %>% 
  write_rds("procedures-lists/lf_vag_msdrg.rds")

vag_msdrg_list %>% nrow()
```

### Vaginal APR_DRG codes

```{r vag_aprdrg}
vag_aprdrg_list <- c(
  "541",
  "542",
  "560"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(vag_aprdrg = value)

vag_aprdrg_list %>% 
  write_rds("procedures-lists/lf_vag_aprdrg.rds")

vag_aprdrg_list %>% nrow()

```

### Vaginal birth exclusions

```{r vag_excl}
vag_excl_list <- c(
  "O660"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(vag_excl = value)

vag_excl_list %>% 
  write_rds("procedures-lists/lf_vag_excl.rds")

vag_excl_list %>% nrow()
```

### Episiotomy

```{r epi}
epi_list <- c(
  "0W8NXZZ"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(epi = value)

epi_list %>% 
  write_rds("procedures-lists/lf_epi.rds")

epi_list %>% nrow()
```

