---
title: "Process various data lists"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

This THCIC analysis will need various lists of columns and ICD-10 codes. This notebook will define them and write them to rds where they can be use in later analysis.

Of note, to turn a single-column rds import into a vector, use the following:

```txt
new_list <- read_rds("procedures-lists/filename.rds") %>% pull(col_name_from_df)

# or

new_list <- read_rds("procedures-lists/filename.rds") %>% .$col_name_from_df

```

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
```

## THCIC column lists

The diagnostic and surgical procedure columns from the THCIC data are frequently used in `case_when()` statements and other vectors. This writes them to csv and rds for use later.

### Import test data for column generation

```{r}
testdata <- read_rds("data-test/ahrq_del_ucmp_ptest.rds")
```

### Diagnostic columns

Values are all the names of diagnostics columns from the data in a singe tibble with column named `diag`. 

```{r}
cols_diag <- testdata %>% 
  select(contains("_DIAG"), -starts_with("POA")) %>%
  names() %>% 
  tibble::enframe(name = NULL) %>% 
  rename(diag = value)

cols_diag %>% 
  write_csv("procedures-lists/cols_diag.csv")

cols_diag %>% 
  write_rds("procedures-lists/cols_diag.rds")
  
```

### Surgical procedure columns

Values are all the names of surgical procedure columns from the data in a singe tibble with column named `surg`.

```{r}
cols_surg <- testdata %>% 
  select(contains("SURG_PROC_CODE")) %>%
  names() %>% 
  tibble::enframe(name = NULL) %>% 
  rename(surg = value)

cols_surg %>% 
  write_csv("procedures-lists/cols_surg.csv")

cols_surg %>% 
  write_rds("procedures-lists/cols_surg.rds")
```

## AHRQ lists

These can come from IQI 33 or IQI 21. Some are in both.


### All deliveries (DELOCMD)

All deliveries, identified by any-listed ICD-10-CM diagnosis code for outcome of delivery (DELOCMD). In both IQI 33 or IQI 21.

```{r}
delocmd_list <- c(
  "Z370",
  "Z371",
  "Z372",
  "Z373",
  "Z374",
  "Z3750",
  "Z3751",
  "Z3752",
  "Z3753",
  "Z3754",
  "Z3759",
  "Z3760",
  "Z3761",
  "Z3762",
  "Z3763",
  "Z3764",
  "Z3769",
  "Z377",
  "Z379"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(delocmd = value)

delocmd_list %>% 
  write_rds("procedures-lists/ahrq_delocmd.rds")

delocmd_list
```

### Cesarean delivery MS-DRG codes: (PRCSE2G)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated. Also in IQI 21 Cesarean Delivery Rate, Uncomplicated.

```{r}
# MS-DRG codes for Cesarean delivery (PRCSE2G*)
prcse2g_list <- c(
  "765",
  "766"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prcse2g = value)

prcse2g_list %>% 
  write_rds("procedures-lists/ahrq_prcse2g.rds")

prcse2g_list
```

### Hysterotomy procedure codes: (PRCSE2P)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated. Also in IQI 21 Cesarean Delivery Rate, Uncomplicated.

```{r}
prcse2p_list <- c(
  "10A00ZZ",
  "10A03ZZ",
  "10A04ZZ"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prcse2p = value)

prcse2p_list %>% 
  write_rds("procedures-lists/ahrq_prcse2p.rds")

prcse2p_list
```

### Cesarean delivery procedure codes: (PRCSECP)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated. Also in IQI 21 Cesarean Delivery Rate, Uncomplicated.

```{r}
prcsecp_list <- c(
  "10D00Z0",
  "10D00Z1",
  "10D00Z2"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prcsecp = value)

prcsecp_list %>% 
  write_rds("procedures-lists/ahrq_prcsecp.rds")

prcsecp_list
```

### Outcome of delivery diagnosis codes: (DELOCMD)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated. Also in IQI 21 Cesarean Delivery Rate, Uncomplicated.

```{r}
delocmd_list <- c(
  "Z370",
  "Z371",
  "Z372",
  "Z373",
  "Z374",
  "Z3750",
  "Z3751",
  "Z3752",
  "Z3753",
  "Z3754",
  "Z3759",
  "Z3760",
  "Z3761",
  "Z3762",
  "Z3763",
  "Z3764",
  "Z3769",
  "Z377",
  "Z379"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(delocmd = value)

delocmd_list %>% 
  write_rds("procedures-lists/ahrq_delocmd.rds")

delocmd_list
```

### Previous Cesarean delivery diagnosis codes: (PRVBACD)

As defined in 1Q1 33 Primary Cesarean Delivery Rate, Uncomplicated

- with any-listed ICD-10-CM diagnosis codes for previous Cesarean delivery (PRVBACD*)

```{r}
prvbacd_list <- c(
  "O3421",
  "O34211",
  "O34212",
  "O34219",
  "O6641"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(prvbacd = value)

prvbacd_list %>% 
  write_rds("procedures-lists/ahrq_prvbacd.rds")

prvbacd_list
```

## Other lists used

### Child-bearing age codes

Researchers at the Office of Health Affairs-Population Health, The University of Texas System work with the THCIC file daily and they suggest filtering deliveries to women of normal child-bearing age, 15-49.

The codes for the ages 15-49 include 05-12. For HIV or drug patients it includes 23 (18-44 yrs).

```{r}
age_list <- c(
  "05",
  "06",
  "07",
  "08",
  "09",
  "10",
  "11",
  "12",
  "23"
) %>%  
  tibble::enframe(name = NULL) %>% 
  rename(age = value)

age_list %>% 
  write_rds("procedures-lists/utoha_age.rds")

age_list

```


