---
title: "THCIC deliveries processing"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

The purpose of this notebook is to process multiple quarters of [THCIC in-patient public use data files](https://www.dshs.texas.gov/thcic/hospitals/Inpatientpudf.shtm) into a single data file of deliveries without complications. This requires importing and applying several filtering options.

We are using AHRQ's [Inpatient Quality Indicator 21 (IQI 21) Cesarean Delivery Rate, Uncomplicated](resources/IQI_21_Cesarean_Delivery_Rate_Uncomplicated.pdf) method, so in this notebook we'll be applying the "DENOMINATOR" rules to identify deliveries and filter out complications and missing/nonrelevant rows. One addition is to filter by women of normal child-bearing age: 15-49.

The output is all uncomplicated deliveries, which we can then analyzed in future files.

Of note, there is another notebook `01-process-test` that uses the same filtering criteria but prints examples at various stages for manual checking.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(fs)
library(tidyverse)
```

## Creating files lists

I have a set of test data that grabs the first 10,000 rows from the first quarter of 2016-2018.

```{r}
# set up test data
test_data_dir <- "data-test"
test_tsv_files <- dir_ls(test_data_dir, recurse = TRUE, regexp = "test_base1")
test_tsv_files
```

Production data

```{r}
# set up production data
data_dir <- "data-raw"
tsv_files <- dir_ls(data_dir, recurse = TRUE, regexp = "PUDF_base1_")

# peek at the captured file list
tsv_files
```

## Function to filter for deliveries

For processing this data, I build functions to apply difference AHRQ filtering to each file before binding them into a single tibble. In some cases the processing filters multiple columns for multiple conditions.

The functions are set up first, then used later in the processing loop.

### Filter to birth deliveries

In this case, we are looking at all columns with "DIAG" in name for values in the `delivery_icd` list, which comes from "DELOCMD" in our IQI 21 or IQI 33 reference.


```{r deliveries}
delocmd_list <- read_rds("procedures-lists/ahrq_delocmd.rds") %>% .$delocmd

filter_del <- function(.data) {
  .data %>%
    filter_at(
      vars(
        matches("_DIAG"),
        -starts_with("POA")
      ),
      any_vars(
        . %in% delocmd_list
      )
    )
}

```

## Exclusions from the deliveries

The AHRQ IQI 21 and IQI 33 requires excluding some complicated delivery cases:

- with any listed ICD-10-CM diagnosis codes for abnormal presentation, fetal death, or multiple gestation (Appendix A: PRCSECD) and
- with missing gender (SEX=missing), age (AGE=missing), quarter (DQTR=missing), year (YEAR=missing) or principal diagnosis (DX1=missing)

### Get PRCSECD list

We first need the list of PRCSECD codes from `resources/IQI_Appendix_A_2019.pdf`: "Abnormal presentation, fetal death and multiple gestation diagnosis codes: (PRCSECD)."

The list of codes was extracted from the PDF and cleaned in OpenRefine to get full list. Details in the `procedures/iqi-appendex-a` folder.

#### Import list of PRCSECD codes

```{r}
# read in the file
prcsecd <- read_csv("procedures/iqi-appendex-a/IQI_Appendix_A.csv")

# number of codes
prcsecd %>% nrow()

# turn it into a list
prcsecd_list <- prcsecd %>% .$codes
```

#### Filter out deliveries based on PRCSECD codes

In defining this function we are filtering for the codes, but retaining the remainder. So, to the filter for the negative, we have to consider "all_vars" instead of "any_vars".

```{r prcsecd}

filter_prcsecd <- function(.data) {
  .data %>%
    filter_at(
      vars(
        contains("_DIAG"),
        -starts_with("POA")
      ),
      all_vars(
        !(. %in% prcsecd_list)
      )
    )
}
```

### Filter out blank cells per Appendix A

Again, from AHRQ's IQI 21 definition:

"with missing gender (SEX=missing), age (AGE=missing), quarter (DQTR=missing), year (YEAR=missing) or principal diagnosis (DX1=missing)."

In base1, the fields are `SEX_CODE`, `PAT_AGE`, `DISCHARGE` for both quarter and year, and `PRINC_DIAG_CODE`.

```{r clean}

filter_appendix_a <- function(.data) {
  .data %>% 
      filter(
        SEX_CODE == "F",
        PAT_AGE != "`",
        RACE != "`",
        !is.na(DISCHARGE),
        !is.na(PRINC_DIAG_CODE)
      )
}
```

### Child-bearing age

Researchers at the Office of Health Affairs-Population Health, The University of Texas System work with the THCIC file daily and they suggest filtering deliveries to women of normal child-bearing age, 15-49.

The codes for the ages 15-49 include 05-12. For HIV or drug patients it includes 23 (18-44 yrs).

This function filters for those values.

```{r age}
age_list <- read_rds("procedures-lists/utoha_age.rds") %>% .$age

function_age <- function(.data) {
  .data %>% 
    filter(PAT_AGE %in% age_list)
}
```

## Import and process

This is the workhorse process to loop through the files and combine the data. It brings in each file and then applies the filtering functions and the appends the results.

At this time, our analysis utilizes only one (PUDF_base1) of several files in the release for each quarter. The raw data is never changed.

Of note:

- There is a trailing tab on each row, which brings in an unnecssary column. This is removed with `col_skip()`, though you will see them as `problems()` in the import output. Those problems are resolved with the `col_skip()` function.
- We set default type as chars because some cols will appear as logical because of the datatype sniffer with readr. We reset necessary cols as `as.numeric` where necessary.

Import warnings are supressed. The hides import errors like `Missing column names filled in: 'X167'` from extra tabs in raw files.

```{r process, echo=T, results='hide', message=F, warning=F}
# warnings supressed.

# create the tibble
data <- tibble()

# set the files list
# use test_tsv_files for testing
files <- tsv_files

for (file in files) {
  c <- read_tsv(
    file,
    col_types = cols(
      .default = col_character(),
      X168 = col_skip(),
      X167 = col_skip()
    )
  ) %>% 
  mutate_at(
    vars(contains("_CHARGES")), as.numeric
  ) %>%
  filter_del() %>% 
  filter_prcsecd() %>% 
  filter_appendix_a %>% 
  function_age
  data <- bind_rows(data, c)
}

data %>% nrow()
```

The result of this is `data` which is our combined and filtered data.

## Add year column

In the resulting file we add a YR column for convenience to use in later analysis.

```{r}
data <- data %>% 
  mutate(
    YR = substr(DISCHARGE, 1, 4)
  )

data %>% 
  count(YR)
```

## Remove other years

Because of a reporting lag, there are years in the original data that we are not using for our analysis. At some point in 2015 there was a switch from ICD-9 to ICD-10 coding, so going eariler would require some conversions. Not impossible, but not in scope at this time to ease complication.

We are using only year 2016-2018. 

```{r}
data <- data %>% 
  filter(YR %in% c("2016", "2017", "2018"))
```

## Write file

We write a single file of the uncomplicated deliveries.

```{r write}
data %>% write_rds("data-processed/ahrq_del_ucmp.rds")

data %>% nrow()

# A klaxon to indicate the processing is complete
beepr::beep(4)

```

