---
title: "AHRQ all deliveries processing"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

The purpose of this notebook is to process multiple quarters of [THCIC in-patient public use data files](https://www.dshs.texas.gov/thcic/hospitals/Inpatientpudf.shtm) into a single data file of all births. This requires importing and applying several filtering options.

We are using AHRQ's [IQI 33 Primary Cesarean Delivery Rate, Uncomplicated](https://qualityindicators.ahrq.gov/Downloads/Modules/IQI/V2019/TechSpecs/IQI_33_Primary_Cesarean_Delivery_Rate_Uncomplicated.pdf) method to define a birth, but do not apply further filtering for complicaitons. We do apply some data filtering/cleaning for missing data as outlined in IQI 33.

The output is all `data-processed/ahrq_del_all.rds`, which we can then analyzed in future files.

Of note, there is another notebook `01-process-test` that uses the same filtering criteria but prints examples at various stages for manual checking.

Also, there is another notebook `00-process-lists` where various AHRQ lists of ICD-10 and other codes are defined separately. Those values are written out to the `procedures-lists` folder as .rds and .csv files and then imported into this notebook and others. See that notebook to inspect the lists. It must be run before this notebook as outputs are used here.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(fs)
library(tidyverse)
```

## Data sources

### Test data

I have a set of test data that grabs the first 10,000 rows from the first quarter of 2016-2019. This is used to test the processing without the load of the production data, which is considerable.

```{r dir_test}
# set test_flag = TRUE to use test data
test_flag <- F
data_dir_test <- "data-test"
tsv_files_test <- dir_ls(data_dir_test, recurse = TRUE, regexp = "test_base1")
tsv_files_test
```

### Production data

Part of this process is to loop through all the matching files in the `data-raw` folder to process them. This sets up those directories.

```{r dir_prod}
# set up production data
data_dir <- "data-raw"
tsv_files <- dir_ls(data_dir, recurse = TRUE, regexp = "PUDF_base1_")

# peek at the captured file list
tsv_files
```

## Function to filter for deliveries

For processing this data, I build functions to apply different AHRQ filtering to each file before binding them into a single tibble. In some cases the functions filter multiple columns for multiple variables.

The functions are set up first, then used later in the processing loop.

### Filter for birth deliveries

In this case, we are looking at all the diagnostic columns for values in the `delocmd_list` list, which comes from "DELOCMD" in the AHRQ IQI 33 reference.

```{r fun_del}
delocmd_list <- read_rds("procedures-lists/ahrq_delocmd.rds") %>% .$delocmd

filter_del <- function(.data) {
  .data %>%
    filter_at(
      vars(
        matches("_DIAG"),
        -starts_with("POA")
      ),
      any_vars(
        . %in% delocmd_list
      )
    )
}
```


### Filter out missing data

Again, from AHRQ's IQI 33 definition:

"with missing gender (SEX=missing), age (AGE=missing), quarter (DQTR=missing), year (YEAR=missing) or principal diagnosis (DX1=missing)."

In base1, the fields are `SEX_CODE`, `PAT_AGE`, `DISCHARGE` for both quarter and year, and `PRINC_DIAG_CODE`.

```{r fun_clean}
filter_clean <- function(.data) {
  .data %>% 
      filter(
        SEX_CODE == "F",
        PAT_AGE != "`",
        RACE != "`",
        !is.na(DISCHARGE),
        !is.na(PRINC_DIAG_CODE)
      )
}
```

### Child-bearing age

Researchers at the Office of Health Affairs-Population Health, The University of Texas System work with the THCIC file daily and they suggest filtering deliveries to women of normal child-bearing age, 15-49.

The codes for the ages 15-49 include "05" through "12". For HIV or drug patients it includes "23" (18-44 yrs).

This function filters for those values.

```{r fun_age}
age_list <- read_rds("procedures-lists/utoha_age.rds") %>% .$age

filter_age <- function(.data) {
  .data %>% 
    filter(PAT_AGE %in% age_list)
}
```

## Import and process

This is the workhorse process to loop through the files and combine the data. It brings in each file and then applies the filtering functions above and then appends the results to the growing tibble.

At this time, the analysis utilizes only one (PUDF_base1) of several files in the release for each quarter. The raw data is never changed.

Of note:

- There is a trailing tab on each row in the data, which creates an unnecssary column. This is removed with `col_skip()` in the import statement, though it is still reported in the `problems()` function. Those problems are resolved with the `col_skip()` function.
- The import sets "col_character" as the default datatype because some columns were otherwise importing as "logical" by the datatype sniffer in readr. Numeric columns are later reset with `as.numeric` where necessary.

Import warnings are supressed. This hides import errors like `Missing column names filled in: 'X167'` caused by the extra tabs in the raw files.

```{r process, echo=T, results='hide', message=F, warning=F}
# warnings supressed.

# create the tibble
data <- tibble()

# set the files list
if(test_flag == T) files <- tsv_files_test else files <- tsv_files

for (file in files) {
  c <- read_tsv(
    file,
    col_types = cols(
      .default = col_character(),
      X168 = col_skip(),
      X167 = col_skip()
    )
  ) %>% 
  mutate_at(
    vars(contains("_CHARGES")), as.numeric
  ) %>%
  filter_del() %>% 
  filter_clean %>% 
  filter_age
  data <- bind_rows(data, c)
}

data %>% nrow()
```

The result of this function is `data`, which is our combined and filtered data.

## Add year column

In the resulting file we add a YR column for convenience to use in later analysis.

```{r add_yr}
data <- data %>% 
  mutate(
    YR = substr(DISCHARGE, 1, 4)
  )

data %>% 
  count(YR)
```

## Remove other years

Because of a reporting lag, there are years in the original data that we are not using for our analysis. At some point in 2015 there was a switch from ICD-9 to ICD-10 coding, so going earlier would require some conversions. Not impossible, but not in scope at this time to ease complication.

We are using full years from 2016-2018 and a partial year 2019 through the 3rd quarter release. 

```{r filter_yr}
data <- data %>% 
  filter(YR %in% c("2016", "2017", "2018", "2019"))
```

## Write file

We write a single file of the uncomplicated deliveries.

```{r write}
if(test_flag == T) write_path <- "data-test/ahrq_del_all_loop_test.rds" else write_path <- "data-processed/ahrq_del_all.rds"

data %>% write_rds(write_path)

data %>% nrow()

# A klaxon to indicate the processing is complete
beepr::beep(4)

```

