---
title: "AHRQ deliveries process comparison"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

This notebook compares the output of a non-looped process to a single process on the data. This sort of tests the function in the `01-ahrq-del-process-loop` file to make sure the less verbose functions process correctly.

The `01-ahrq-del-process-test` notebook use a non-looped processesing of the data with some visual checks on the files. I want to make sure those same filters are applied to the looping notebook above used for production.

I ran a test on the looped processes against the test data for comparison. Here I check to make sure the number of rows returned is the same.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
```

Read in each test rds and note the number of rows. The result should be the same for both.

```{r}
ttst <- read_rds("data-test/ahrq_del_all_loop_test.rds")
ttst %>% nrow()
ptst <- read_rds("data-test/ahrq_del_all_single_test.rds")
ptst %>% nrow()
```

I once had a problem with the age filtering in the no-loop file, so this checks that. There should be zero rows returned here.

```{r echo=F, message=F}
ttst %>% anti_join(ptst) %>% 
  select(PAT_AGE)
```

