---
title: "Doctor deliveries per hospital (AHRQ specs), 2016-3q2019"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

By **Christian McDonald**, Assistant Professor of Practice\
School of Journalism, Moody College of Communication\
University of Texas at Austin

## Purpose of this analysis

The purpose of this notebook is to look at the number of deliveries per doctor and some subsets of that, answering the following questions:

- How many doctors per hospital are doing deliveries and how many deliveries do they do each year?
- Of all deliveries in a year, what percentage of women who went in to give birth got an episiotomy or C-section. Both statewide, and for hospitals of interest.

I DO NOT filter for complications, fetal deaths or other factors. This could be revisited later, but the idea is to see how many people are served for these procedures regardless of complications.

I use the `ATTENDING_PHYSICIAN_UNIF_ID` field to identify the attending physician, described as "Unique identifier assigned to the licensed physician expected to certify medical necessity of services rendered, with primary responsibility for the patient’s medical care and treatment." That indication does not guarantee the doctor performed a specific procedure.

There is also a `OPERATING_PHYSICIAN_UNIF_ID` field for each patient: "Unique identifier assigned to the operating physician or physician other than the attending physician."

> Both of the PHYSICIAN values are suppressed if there are fewer than 5 in a quarter, or if the license was temporary our could not be matched. That appears to be a significant suppression for many hospitals.

As I understand these, there is no guarantee that either doctor actually performed a specific procedure, but the ATTENDING PHYSICIAN should be responsible for the patient's care.

## Project setup

```{r setup, echo=T, results='hide', message=F, warning=F}
library(fs)
library(tidyverse)
library(dplyr)
library(janitor)
library(DT)
```

### Import all deliveries

I start with a subset of the [THCIC in-patient public use data files](https://www.dshs.texas.gov/thcic/hospitals/Inpatientpudf.shtm) that include all deliveries as outlined in AHRQ's [Inpatient Quality Indicators Technical Specifications](https://www.qualityindicators.ahrq.gov/Modules/IQI_TechSpec_ICD10_v2019.aspx). The `DELOCMD` specification in IQI 21 is "All deliveries, identified by any-listed ICD-10-CM diagnosis code for outcome of delivery". Some cleaning was applied as outlined in the `01-process-ahrq-del-loop` notebook. The result is imported here.

(I also have test data options, which is a small subset of the data for faster processing in testing.)

```{r imports}
test_flag <- F

### test data
path_test <- "data-test/ahrq_del_all_loop_test.rds"

### production data
path_prod <- "data-processed/ahrq_del_all.rds"

### import based on flag
if (test_flag == T) del <- read_rds(path_test) else del <- read_rds(path_prod)

del %>% nrow()
```

### Set up various processing lists

These are lists from various AHRQ and Leapfrog definitions. See 01-process-lists for details.

```{r lists}
# Cesarean delivery MS-DRG codes, updated
prcse2g_v2_list <- read_rds("procedures-lists/ahrq_prcse2g_v2.rds") %>% .$prcse2g
prcse2g_v2_list

# Episiotomy codes
epi_list <- read_rds("procedures-lists/lf_epi.rds") %>% .$epi
epi_list

# surgical procedure columns
surg_cols <- read_rds("procedures-lists/cols_surg.rds") %>% .$surg

# Updated Hospitals list
providers_list <- read_rds("procedures-lists/providers_cleaned.rds")
```

### Update PROVIDER_NAME

Hospitals change names over time, skewing any analysis that groups by PROVIDER_NAME. This process updates the PROVIDER_NAME field to use the most recent name used in the data, based on a sanitized list from another workbook.

```{r providers_list}
del <- del %>% 
  left_join(providers_list, by = "THCIC_ID") %>% 
  select(-PROVIDER_NAME) %>% 
  rename(PROVIDER_NAME = PROVIDER_NAME_CLEANED)
```

### Cesarean indicator

Later we want to get rates by doctor for Cesarean deliveries. I create a marker column so we can do that.

[AHRQ Inpatient Quality Indicator](https://www.qualityindicators.ahrq.gov/Modules/IQI_TechSpec_ICD10_v2019.aspx) for [Cesarean Delivery Rate, Uncomplicated (IQI 21)](https://www.qualityindicators.ahrq.gov/Downloads/Modules/IQI/V2019/TechSpecs/IQI_21_Cesarean_Delivery_Rate_Uncomplicated.pdf) defines a Cesarean delivery as such.

- I use the MS-DRG codes for Cesarean delivery (PRCSE2G) to define any Cesarean case.
- I do NOT apply the PRCSECD exclusions here because we want all Cesareans, complicated or not. The exclusions of missing gender, etc. are applied on the original data before importing here.

```{r csec_col}
del <- del %>% 
  mutate(
    PRCSE2G = if_else(MS_DRG %in% prcse2g_v2_list, T, F)
  )

# peek at result
del %>% 
  count(PRCSE2G) %>% 
  rename(CASES = n)
```

### Episiotomy indicator

I use the [2019 Leapfrog Hospital Survey p103](https://www.leapfroggroup.org/sites/default/files/Files/2019HospitalSurvey_20190529_v8.0%20%28version%203%29.pdf) for the episiotomy definition. Of note is we are applying this to all deliveries as defined by AHRQ instead of Leapfrog's original definition. The definition difference should be minimal.

```{r epi_col}
# list of codes for episiotomy, which is really one: 0W8NXZZ
del <- del %>% 
  mutate(
    EPI = case_when(
      PRINC_SURG_PROC_CODE %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_1 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_2 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_3 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_4 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_5 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_6 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_7 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_8 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_9 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_10 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_11 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_12 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_13 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_14 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_15 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_16 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_17 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_18 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_19 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_20 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_21 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_22 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_23 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_24 %in% epi_list ~ TRUE,
      TRUE ~ FALSE
    )
  )

del %>% 
  count(EPI) %>% 
  rename(RECORD = n)
```

> At this point our data is processed.

---

## Dealing with doctor suppressions

Both ATTENDING_PHYSICIAN_UNIF_ID and OPERATING_PHYSICIAN_UNIF_ID are "Suppressed when the number of physicians represented in a DRG for a hospital is less than the minimum cell size of five."

- 9999999998: Cell size less than 5
- 9999999999: Temporary license or license number could not be matched

I create a variable to measure suppressions, and then count the difference.

```{r supp_look}
suppressed = c("9999999998", "9999999999")

del %>% 
  mutate(
    PSUPP = if_else(ATTENDING_PHYSICIAN_UNIF_ID %in% suppressed, T, F)
  ) %>% 
  tabyl(PSUPP) %>% 
  rename(count = n) %>% 
  adorn_pct_formatting()
```

The ATTENDING_PHYSICIAN is suppressed in 6.4% of deliveries. For some hospitals, like Brownwood Regional Medical Center, all the physician data is suppressed.

```{r supp_count}
del %>% 
  filter(str_detect(PROVIDER_NAME, "Brownwood Regional Medical Center")) %>% 
  mutate(
    PSUPP = if_else(ATTENDING_PHYSICIAN_UNIF_ID %in% suppressed, T, F)
  ) %>% 
  tabyl(PSUPP) %>% 
  rename(count = n) %>% 
  adorn_pct_formatting()
```

Since our hospitals of interest are in Laredo, let's check how many of those are suppressed as well.

```{r supp_count_laredo}
del %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo")) %>% 
  mutate(
    PSUPP = if_else(ATTENDING_PHYSICIAN_UNIF_ID %in% suppressed, T, F)
  ) %>% 
  tabyl(PSUPP, PROVIDER_NAME) %>% 
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns()
```

### Removing suppressed doctors

To achieve a count of deliveries per doctor, I remove the records where the ATTENDING_PHYSICIAN was suppressed as this could combine multiple doctors into the same group. This supression may have more affect on some hospitals than others.

```{r del_supp}
del_supp <- del %>% 
  filter(
    !ATTENDING_PHYSICIAN_UNIF_ID %in% suppressed
  )
```

## Deliveries per hospital, per doctor

How many deliveries by hospitals from 2016 to present. This is from the data where unknown doctors are suppressed, but does NOT filter for doctors who did few deliveries.

```{r del_hosp_doc}
del_supp %>% 
  group_by(PROVIDER_NAME) %>% 
  summarize(
    DELIVERIES = n(),
    PHYSICIANS = n_distinct(ATTENDING_PHYSICIAN_UNIF_ID)
    ) %>% 
  mutate(
    RATE = round_half_up(DELIVERIES/PHYSICIANS, 1)
  ) %>% 
  arrange(RATE %>% desc()) %>% 
  datatable()
```

### Difference removing infrequent deliveries

In this view I remove doctors with fewer than 20 deliveries in a given year to give a more accurate look at the staff doctors that do the bulk of deliveries.

> The choice of 20 deliveries as a threshold is arbitrary and could be changed if we deem necessary.

```{r del_hosp_doc_freq}
del_supp %>% 
  group_by(YR, PROVIDER_NAME, ATTENDING_PHYSICIAN_UNIF_ID) %>% 
  summarize(DELIVERIES = n()) %>% 
  rename(PHYSICIAN = ATTENDING_PHYSICIAN_UNIF_ID) %>% 
  filter(DELIVERIES >= 20) %>% 
  group_by(PROVIDER_NAME) %>% 
  summarize(
    DELIVERIES = sum(DELIVERIES),
    PHYSICIANS = n_distinct(PHYSICIAN)
  ) %>% 
  mutate(
    RATE = round_half_up(DELIVERIES/PHYSICIANS,1)
  ) %>% 
  arrange(RATE %>% desc()) %>% 
  datatable()
```

### Deliveries per doctor at Laredo hospitals

Delivery rate per doctor by year. Unknown doctors are suppressed. Infrequent deliveries (<20/year) are filtered out.

```{r del_hosp_doc_freq_yr_laredo}
del_supp %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo")) %>%
  group_by(YR, PROVIDER_NAME, ATTENDING_PHYSICIAN_UNIF_ID) %>% 
  summarize(DELIVERIES = n()) %>% 
  rename(PHYSICIAN = ATTENDING_PHYSICIAN_UNIF_ID) %>% 
  filter(DELIVERIES >= 20) %>% 
  group_by(YR, PROVIDER_NAME) %>% 
  summarize(
    DELIVERIES = sum(DELIVERIES),
    PHYSICIANS = n_distinct(PHYSICIAN)
  ) %>% 
  mutate(
    RATE = round_half_up(DELIVERIES/PHYSICIANS, 1)
  ) %>% 
  select(YR, PROVIDER_NAME, RATE) %>% 
  pivot_wider(names_from = YR, values_from = RATE)
```

Just how much do doctor suppressions affect these rates in Laredo? We'll do the same calculation on the data but without suppressig unknown doctors. Note this has limitations because multiple doctors could be counted in the two suppression values.

```{r del_hosp_doc_freq_yr_laredo_nosupp}
del %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo")) %>%
  group_by(YR, PROVIDER_NAME, ATTENDING_PHYSICIAN_UNIF_ID) %>% 
  summarize(DELIVERIES = n()) %>% 
  rename(PHYSICIAN = ATTENDING_PHYSICIAN_UNIF_ID) %>% 
  filter(DELIVERIES >= 20) %>% 
  group_by(YR, PROVIDER_NAME) %>% 
  summarize(
    DELIVERIES = sum(DELIVERIES),
    PHYSICIANS = n_distinct(PHYSICIAN)
  ) %>% 
  mutate(
    RATE = round_half_up(DELIVERIES/PHYSICIANS, 1)
  ) %>% 
  select(YR, PROVIDER_NAME, RATE) %>% 
  pivot_wider(names_from = YR, values_from = RATE)
```
## Cesarean rates by hospital

Here we look at all deliveries to see how many mothers have Cesareans. Note this starts with all ATTENDING_PHYSICIANS, including those who's IDs are suppressed. These are also all Cesareans, complicated or not. This is a simple rate of Cesarean births / All births in order to get an idea how many are performed.

Excludes hospitals with fewer than 300 deliveries in our time span.

```{r csec_rate_hosp}
csec_rate_hosp <- del %>% 
  group_by(PROVIDER_NAME, PRCSE2G) %>% 
  count(PRCSE2G) %>% 
  rename(CASES = n) %>%
  pivot_wider(names_from = PRCSE2G, values_from = CASES) %>% 
  rename(NCSEC = "FALSE", CSEC = "TRUE") %>% 
  mutate(
    TOTAL = NCSEC + CSEC,
    RATE = round_half_up((CSEC / TOTAL) * 100, 1)
  ) %>% 
  filter(
    TOTAL >= 300 
  ) %>% 
  arrange(RATE %>% desc())

csec_rate_hosp %>% 
  datatable()
```

### Cesearean rate for Laredo

```{r csec_rate_hosp_laredo}
csec_rate_hosp %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```

### Cesarean rates by hospital by year

This is the same calculation as above, but by year, showing only the rates. Excludes hospitals with fewer than 100 deliveries in a year.

```{r csec_hosp_rate_yr}
csec_hosp_rate_yr <- del %>% 
  group_by(YR, THCIC_ID, PROVIDER_NAME, PRCSE2G) %>% 
  count(YR, PRCSE2G) %>%
  rename(CASES = n) %>%
  pivot_wider(names_from = PRCSE2G, values_from = CASES) %>%
  rename(NCSEC = "FALSE", CSEC = "TRUE") %>%
  mutate(
    TOTAL = NCSEC + CSEC,
    RATE = round_half_up((CSEC / TOTAL) * 100, 1)
  ) %>%
  filter(
    TOTAL >= 100
  )
```

Present the rate as table.

```{r csec_hosp_rate_yr_table}
csec_hosp_rate_yr_table <- csec_hosp_rate_yr %>%
  select(THCIC_ID, YR, PROVIDER_NAME, RATE) %>%
  pivot_wider(names_from = YR, values_from = RATE) %>%
  arrange(`2019` %>% desc())

csec_hosp_rate_yr_table %>% 
  datatable()
```


### Cesarean rates by year for Laredo

```{r csec_hosp_rate_yr_laredo}
csec_hosp_rate_yr_table %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```


## Episiotomy rates

Like the simple Cesarean rate above, here we look at all deliveries and note how many involved episiotomies. Note this starts with all ATTENDING_PHYSICIANS, including those who's IDs are suppressed. Excludes hospitals with fewer than 300 deliveries in our time span.

```{r epi_rate_hosp}
epi_rate_hosp <- del %>% 
  group_by(PROVIDER_NAME, EPI) %>% 
  count(EPI) %>% 
  rename(CASES = n) %>% 
  pivot_wider(names_from = EPI, values_from = CASES) %>% 
  rename(
    EPI = "TRUE",
    NEPI = "FALSE"
  ) %>% 
  mutate(
    TOTAL = NEPI + EPI,
    RATE = round_half_up((EPI / TOTAL * 100), 1)
  ) %>% 
  filter(TOTAL >= 300) %>% 
  arrange(RATE %>% desc())

epi_rate_hosp %>% 
  datatable()
```

### Episiotomy rate for Laredo hospitals

```{r epi_rate_hosp_laredo}
epi_rate_hosp %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```

## Episiotomy rates by hospital by year

```{r epi_rate_hosp_yr}
epi_rate_hosp_yr <- del %>% 
  group_by(YR, PROVIDER_NAME, EPI) %>% 
  count(YR, EPI) %>% 
  rename(CASES = n) %>% 
  pivot_wider(names_from = EPI, values_from = CASES) %>% 
  rename(NEPI = "FALSE", EPI = "TRUE") %>% 
  mutate(
    TOTAL = NEPI + EPI,
    RATE = round_half_up((EPI / TOTAL) * 100, 1)
  ) %>% 
  filter(
    TOTAL >= 100 
  ) %>% 
  select(YR, PROVIDER_NAME, RATE) %>% 
  pivot_wider(names_from = YR, values_from = RATE) %>% 
  arrange(`2019` %>% desc())

epi_rate_hosp_yr %>% 
  datatable()
```

### Episiotomy rate by year for Laredo

```{r epi_rate_hosp_yr_laredo}
epi_rate_hosp_yr %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```

## Either Episiotomy or Cesarean

This looks to see if a mother had either a cesarean or an episiotomy. All the same things apply: All doctors, all complications, but hospitals with fewer than 300 deliveries in our time period are excluded.

```{r epicsec_rate_hosp}
epicsec_rate_hosp <- del %>% 
  mutate(
        EPICSEC = if_else((EPI == T | PRCSE2G) == T, T, F)
  ) %>% 
  count(PROVIDER_NAME, EPICSEC) %>% 
  rename(CASES = n) %>% 
  pivot_wider(names_from = EPICSEC, values_from = CASES) %>% 
  rename(
    EPICSEC = "TRUE",
    NEPICSEC = "FALSE"
  ) %>% 
  mutate(
    TOTAL = EPICSEC + NEPICSEC,
    RATE = round_half_up((EPICSEC / TOTAL * 100), 1)
  ) %>% 
  filter(TOTAL >= 300) %>% 
  arrange(RATE %>% desc())

epicsec_rate_hosp %>% 
  datatable()
```

### Either episiotomy or Cesarean for Laredo

```{r epicsec_rate_hosp_laredo}
epicsec_rate_hosp %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```

### Episiotomy or Cesarean rate by hospital by year

```{r epicsec_rate_hosp_yr}
# prep data for export and table
epicsec_rate_hosp_yr <- del %>% 
  mutate(
    EPICSEC = if_else((EPI == T | PRCSE2G) == T, T, F)
  ) %>% 
  count(THCIC_ID, YR, PROVIDER_NAME, EPICSEC) %>% 
  rename(CASES = n) %>% 
  pivot_wider(names_from = EPICSEC, values_from = CASES) %>% 
  rename(
    EPICSEC = "TRUE",
    NEPICSEC = "FALSE"
  ) %>% 
  mutate(
    TOTAL = EPICSEC + NEPICSEC,
    RATE = round_half_up((EPICSEC / TOTAL * 100), 1)
  ) %>% 
  filter(TOTAL >= 100)

# pivot data for table
epicsec_rate_hosp_yr_table <- epicsec_rate_hosp_yr %>% 
  select(THCIC_ID, YR, PROVIDER_NAME, RATE) %>% 
  pivot_wider(names_from = YR, values_from = RATE) %>% 
  arrange(`2019` %>% desc())

epicsec_rate_hosp_yr_table %>% 
  datatable()
```

### Episiotomy or Cesarean rate by year for Laredo

```{r epicsec_rate_hosp_yr_laredo}
epicsec_rate_hosp_yr_table %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```

## Summaries

### Cesarean summary

```{r csec_rate_tx_yr_summary}
csec_rate_tx_yr_summary <- del %>% 
  group_by(YR, PRCSE2G) %>% 
  count(PRCSE2G) %>% 
  rename(CASES = n) %>%
  pivot_wider(names_from = PRCSE2G, values_from = CASES) %>% 
  rename(NCSEC = "FALSE", CSEC = "TRUE") %>% 
  mutate(
    SUMMARY = "TX",
    CATEGORY = "CESAREAN",
    MEASUREMENT = "RATE",
    TOTAL = NCSEC + CSEC,
    VALUE = round_half_up((CSEC / TOTAL) * 100, 1) # RATE
  ) %>% 
  select(YR, SUMMARY, CATEGORY, MEASUREMENT, VALUE)

csec_rate_tx_yr_summary
```

### Episiotomy & Cesarean summary

```{r epicsec_rate_tx_yr_summary}
epicsec_rate_tx_yr_summary <- del %>% 
  mutate(
        EPICSEC = if_else((EPI == T | PRCSE2G) == T, T, F)
  ) %>% 
  group_by(YR, EPICSEC) %>% 
  count(EPICSEC) %>% 
  rename(CASES = n) %>% 
  pivot_wider(names_from = EPICSEC, values_from = CASES) %>% 
  rename(
    EPICSEC = "TRUE",
    NEPICSEC = "FALSE"
  ) %>% 
  mutate(
    SUMMARY = "TX",
    CATEGORY = "EPISIOTOMY OR CESAREAN",
    MEASUREMENT = "RATE",
    TOTAL = EPICSEC + NEPICSEC,
    VALUE = round_half_up((EPICSEC / TOTAL * 100), 1) # RATE
  ) %>% 
  select(YR, SUMMARY, CATEGORY, MEASUREMENT, VALUE)

epicsec_rate_tx_yr_summary
```

### Episiotomy or Cesarean rate by hospital: Averaged, by year

```{r epicsec_rate_hosp_yr_summary}
epicsec_rate_hosp_yr_summary <- epicsec_rate_hosp_yr %>% 
  ungroup() %>% 
  group_by(YR) %>% 
  summarize(
    SUMMARY = "HOSPITAL",
    CATEGORY = "EPI_OR_CSEC",
    MEASUREMENT = "MEAN OF RATE",
    # MEDIAN = median(RATE),
    VALUE = round_half_up(mean(RATE, na.rm = TRUE),1) # MEAN OF RATE
  )

epicsec_rate_hosp_yr_summary
```

## Writing files and closing out

For export:

- csec_hosp_rate_yr: Grouped by id, year and name. Observations are NCSEC (not cesarean), CSEC (cesarean), TOTAL and RATE.
- epicsec_rate_hosp_yr: Grouped by id, year and name. Observations are NEPICSEC (Not either epi or csec), EPICSEC (is either), TOTAL and RATE

Plus summary files for another notebook.

```{r write}

if (test_flag == F) csec_rate_tx_yr_summary %>%
  write_rds("data-processed/csec_rate_tx_yr_summary.rds")

if (test_flag == F) epicsec_rate_tx_yr_summary %>%
  write_rds("data-processed/epicsec_rate_tx_yr_summary.rds")

if (test_flag == F) epicsec_rate_hosp_yr_summary %>%
  write_rds("data-processed/epicsec_rate_hosp_yr_summary.rds")

if (test_flag == F) csec_hosp_rate_yr %>%
  arrange(PROVIDER_NAME) %>%
  write_csv("exports/csec_hosp_rate_yr.csv")

if (test_flag == F) epicsec_rate_hosp_yr %>%
  arrange(PROVIDER_NAME) %>%
  write_csv("exports/epicsec_rate_hosp_yr.csv")




# A klaxon to indicate the processing is complete
beepr::beep(4)
```

