---
title: "Leapfrog Episiotomy rates, 2016-3q2019"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

By **Christian McDonald**, Assistant Professor of Practice\
School of Journalism, Moody College of Communication\
University of Texas at Austin

This analysis looks at episiotomy rates using the [Texas Health Care Information Collection's Texas Inpatient Public Use Data File](https://www.dshs.texas.gov/thcic/hospitals/Inpatientpudf.shtm). The definition to calculate the rates comes from the [2019 Leapfrog Hospital Survey p103](https://www.leapfroggroup.org/sites/default/files/Files/2019HospitalSurvey_20190529_v8.0%20%28version%203%29.pdf). I start with data filtered from the THCIC data using the Leapfrog specs. That process is explained in "01-process-lf-epi-loop".

## Setup and import

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
library(DT)
library(tigris)
```

```{r imports}
test_flag <- F

### test data
path_test <- "data-test/lf_del_vag_loop_test.rds"

### production data
path_prod <- "data-processed/lf_del_vag.rds"

### import based on flag
if (test_flag == T) del_vag_excl <- read_rds(path_test) else del_vag_excl <- read_rds(path_prod)

del_vag_excl %>% nrow()
```

### Update PROVIDER_NAME

Hospitals change names over time, skewing any analysis that groups by PROVIDER_NAME. This process updates the PROVIDER_NAME field to use the most recent name used in the data, based on a sanitized list from another workbook.

```{r providers_list}
# Updated Hospitals list
providers_list <- read_rds("procedures-lists/providers_cleaned.rds")

del_vag_excl <- del_vag_excl %>% 
  left_join(providers_list, by = "THCIC_ID") %>% 
  select(-PROVIDER_NAME) %>% 
  rename(PROVIDER_NAME = PROVIDER_NAME_CLEANED)
```

### Set the episiotomy cases

This creates a column for cases where episiotomy is true. We have to look through each of the surgical procedure columns to check for the code.

> I'd like to refactor this method, but at least it is easy to see and understand.

```{r epi_col}
# list of codes for episiotomy, which is really one: 0W8NXZZ
epi_list <- read_rds("procedures-lists/lf_epi.rds") %>% .$epi
epi_list

lf_epi <- del_vag_excl %>% 
  mutate(
    EPI = case_when(
      PRINC_SURG_PROC_CODE %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_1 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_2 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_3 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_4 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_5 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_6 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_7 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_8 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_9 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_10 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_11 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_12 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_13 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_14 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_15 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_16 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_17 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_18 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_19 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_20 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_21 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_22 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_23 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_24 %in% epi_list ~ TRUE,
      TRUE ~ FALSE
    )
  )

```

This completes the processing of the data.

---

## Searchable table: Episiotomy rates by hospital, combined years

Hospitals with fewer than 300 deliveries excluded.

```{r lf_epi_rate_hosp}
lf_epi_rate_hosp <- lf_epi %>%
  group_by(PROVIDER_NAME, EPI) %>% 
  summarise(
    EPI_CNT = n()
  ) %>% 
  pivot_wider(names_from = EPI, values_from = EPI_CNT) %>% 
  rename(
    EPIF = "FALSE",
    EPIT = "TRUE"
  ) %>% 
  mutate(
    TOTAL = EPIF + EPIT,
    EPIRATE = round_half_up((EPIT / TOTAL) * 100,1)
  ) %>% 
  select(PROVIDER_NAME, TOTAL, EPIF, EPIT, EPIRATE) %>% 
  filter(
    TOTAL >= 300
    ) %>% 
  arrange(EPIRATE %>% desc())

lf_epi_rate_hosp %>%   
    datatable()
```

## Episiotomy rates by hospital, by year

A look at the episiotomy rates for hospitals by year. We create the rate using the EPI column we created above, then pivot to do the math. We pivot again to see the years nicely in a table. Excludes hospitals with fewer than 100 deliveries in a given year.

```{r lf_epi_rate_hosp_yr}
# pivot to crate the rate based on logical EPI column
lf_epi_rate_hosp_yr <- lf_epi %>% 
  group_by(YR, THCIC_ID, PROVIDER_NAME, EPI) %>% 
  summarise(
    EPI_CNT = n()
  ) %>% 
  pivot_wider(names_from = EPI, values_from = EPI_CNT) %>% 
  rename(
    EPIF = "FALSE",
    EPIT = "TRUE"
  ) %>% 
  mutate(
    TOTAL = EPIF + EPIT,
    EPIRATE = round_half_up((EPIT / TOTAL) * 100,1)
  )

# select, pivot to see years.
lf_epi_rate_hosp_yr_table <- lf_epi_rate_hosp_yr %>% 
  filter(TOTAL >= 100) %>% 
  select(YR, THCIC_ID, PROVIDER_NAME, EPIRATE) %>% 
  pivot_wider(names_from = YR, values_from = EPIRATE) %>% 
  arrange(`2019` %>% desc())

lf_epi_rate_hosp_yr_table %>% datatable()
```

## Laredo hospitals

Filtering above sets for Laredo hospitals.

### Episiotomy rate combined years, Laredo hospitals

From combined years of the data.

```{r lf_epi_rate_hosp_laredo}
lf_epi_rate_hosp %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```

### Episiotomy rates by year, Laredo hospitals

The table above, filtered for Laredo.

```{r lf_epi_rate_hosp_yr_table_laredo}
# filter for Laredo
lf_epi_rate_hosp_yr_table %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```

### Chart: Episiotomy rates by year, Laredo

```{r lf_epi_rate_hosp_yr_laredo_plot}
lf_epi_rate_hosp_yr %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo")) %>%
  ggplot(aes(YR, EPIRATE)) +
  geom_line(aes(group = PROVIDER_NAME, color = PROVIDER_NAME)) +
  expand_limits(y = c(0,40)) +
  theme(legend.position="bottom", legend.box = "vertical") +
  labs(title = "Episiotomy rate by year, Laredo hospitals", x = "YEAR", y = "Episiotomy rate")
```

### Chart: Episiotomy rates by quarter, Laredo

```{r lf_epi_rate_hosp_qr_laredo_plot}
lf_epi_rate_hosp_qr_laredo_plot <- lf_epi %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo")) %>%
  group_by(DISCHARGE, PROVIDER_NAME, EPI) %>% 
  summarise(
    EPI_CNT = n()
  ) %>% 
  pivot_wider(names_from = EPI, values_from = EPI_CNT) %>% 
  rename(
    EPIF = "FALSE",
    EPIT = "TRUE"
  ) %>% 
  mutate(
    TOTAL = EPIF + EPIT,
    EPIRATE = round_half_up((EPIT / TOTAL) * 100,1)
  )

lf_epi_rate_hosp_qr_laredo_plot %>% 
  ggplot(aes(DISCHARGE, EPIRATE)) +
  geom_line(aes(group = PROVIDER_NAME, color = PROVIDER_NAME)) +
  expand_limits(y = c(0,40)) +
  theme(legend.position="bottom", legend.box = "vertical",axis.text.x=element_text(angle = -45, hjust = 0)) +
  labs(title = "Episiotomy rate by quarter, Laredo hospitals", x = "QUARTER", y = "Episiotomy rate")
```


## Patient county

Get FIPS codes lookup for county names.

```{r tx_fips}
tx_fips <- fips_codes %>% 
  filter(state == "TX") %>% 
  select(county_code, county)
# peek
tx_fips %>% head(2)
```

### Episiotomies by county, full data

This looks at rates by the patient's county (the hospital could be elsewhere.). Currently not filtered for any minimum caseload since it is a 3+ year period.

```{r lf_epi_rate_county}
lf_epi_rate_county <- lf_epi %>%
  group_by(PAT_COUNTY, EPI) %>% 
  summarise(
    EPI_CNT = n()
  ) %>% 
  # join for county names
  left_join(tx_fips, by=c( "PAT_COUNTY" = "county_code")) %>% 
  ungroup() %>% 
  rename(COUNTY = county) %>% 
  # pivot for mutates
  pivot_wider(names_from = EPI, values_from = EPI_CNT) %>% 
  rename(
    EPIF = "FALSE",
    EPIT = "TRUE"
  ) %>% 
  mutate(
    TOTAL = EPIF + EPIT,
    EPIRATE = round_half_up((EPIT / TOTAL) * 100,1)
  ) %>% 
  select(PAT_COUNTY, COUNTY, TOTAL, EPIF, EPIT, EPIRATE) %>% 
  # filter by total
  # filter(
  #   TOTAL >= 300
  #   ) %>% 
  arrange(EPIRATE %>% desc())

lf_epi_rate_county %>%   
    datatable()
```

### Episiotimies by county, by year

Group by patient county. This table excludes fewer than 10 cases in a county in a given year.


```{r lf_epi_rate_county_yr}
# pivot to crate the rate based on logical EPI column
lf_epi_rate_county_yr <- lf_epi %>% 
  group_by(YR, PAT_COUNTY, EPI) %>% 
  summarise(
    EPI_CNT = n()
  ) %>% 
  # Join to add county names
  left_join(tx_fips, by=c( "PAT_COUNTY" = "county_code")) %>% 
  ungroup() %>% 
  rename(COUNTY = county) %>% 
  pivot_wider(names_from = EPI, values_from = EPI_CNT) %>% 
  rename(
    EPIF = "FALSE",
    EPIT = "TRUE"
  ) %>% 
  mutate(
    TOTAL = EPIF + EPIT,
    EPIRATE = round_half_up((EPIT / TOTAL) * 100,1)) %>% 
    # filter caseload
    filter(TOTAL >= 10)

# select, pivot to see years.
lf_epi_rate_county_yr_table <- lf_epi_rate_county_yr %>% 
  select(YR, COUNTY, EPIRATE) %>% 
  pivot_wider(names_from = YR, values_from = EPIRATE) %>% 
  arrange(`2019` %>% desc())

lf_epi_rate_county_yr_table %>% datatable()
```

## Summaries

### Statewide episiotomy rate

We combine all years of data to compare the percentage of episiotomy cases. The **TRUE** value is the percentage of cases where an episiotomy is performed.

```{r lf_epi_rate_tx}
lf_epi %>% 
  tabyl(EPI) %>% 
  rename(count = n) %>% 
  adorn_pct_formatting()
```

Creating a summary table in case we want it.

```{r lf_epi_rate_tx_summary}
lf_epi_rate_tx_summary <- lf_epi %>% 
  group_by(EPI) %>% 
  summarize(CNT = n()) %>% 
  pivot_wider(names_from = EPI, values_from = CNT) %>% 
  rename(
    EPIF = "FALSE",
    EPIT = "TRUE"
  ) %>% 
  mutate(
    SUMMARY = "TX",
    CATEGORY = "EPISIOTOMY",
    MEASUREMENT = "RATE",
    TOTAL = EPIF + EPIT,
    VALUE = round_half_up((EPIT / TOTAL) * 100,1) # EPIRATE
  ) %>% 
  select(SUMMARY, CATEGORY, MEASUREMENT, VALUE)

lf_epi_rate_tx_summary
```

### Episiotomy rate statewide by year 

```{r lf_epi_rate_tx_yr_summary}
lf_epi_rate_tx_yr_summary <- lf_epi %>%
  group_by(YR, EPI) %>% 
  summarise(
    EPI_CNT = n()
  ) %>% 
  pivot_wider(names_from = EPI, values_from = EPI_CNT) %>% 
  rename(
    EPIF = "FALSE",
    EPIT = "TRUE"
  ) %>% 
  mutate(
    SUMMARY = "TX",
    CATEGORY = "EPISIOTOMY",
    MEASUREMENT = "RATE",
    TOTAL = EPIF + EPIT,
    VALUE = round_half_up((EPIT / TOTAL) * 100,1) # EPIRATE
  ) %>% 
  select(
    YR, SUMMARY, CATEGORY, MEASUREMENT, VALUE
  )

lf_epi_rate_tx_yr_summary
```

### Episiotomy rate by hospital: Averaged, by year

```{r lf_epi_rate_hosp_yr_summary}
lf_epi_rate_hosp_yr_summary <- lf_epi_rate_hosp_yr %>% 
  ungroup() %>% 
  group_by(YR) %>% 
  summarize(
    SUMMARY = "HOSPITAL",
    CATEGORY = "EPISIOTOMY",
    MEASUREMENT = "MEAN OF RATE",
    # MEDIAN = median(EPIRATE),
    VALUE = round_half_up(mean(EPIRATE, na.rm = TRUE),1) #MEAN
  )

lf_epi_rate_hosp_yr_summary
```

## Write files

Writing out aggregate files. Here is a list of CSVs exports:

- lf_epi_rate_hosp_yr: Grouped by YR, PROVIDER NAME. Aggregations are EPIF (Count Epi False), EPIT (Count Epi True), TOTAL (Count of all vaginal deliveries), EPIRATE.
- lf_epi_rate_county_yr: Grouped by YR, PAT_COUNTY, COUNTY. Aggregations are EPIF (Count Epi False), EPIT (Count Epi True), TOTAL (Count of all vaginal deliveries), EPIRATE.


```{r write}
# lf_epi %>% write_rds("data-processed/epi.rds")

if (test_flag == F) lf_epi_rate_tx_yr_summary %>%
  write_rds("data-processed/lf_epi_rate_tx_yr_summary.rds")

if (test_flag == F) lf_epi_rate_hosp_yr_summary %>%
  write_rds("data-processed/lf_epi_rate_hosp_yr_summary.rds")

if (test_flag == F) lf_epi_rate_hosp_yr %>%
  arrange(PROVIDER_NAME,YR) %>%
  write_csv("exports/lf_epi_rate_hosp_yr.csv")

if (test_flag == F) lf_epi_rate_county_yr %>%
  write_csv("exports/lf_epi_rate_county_yr.csv")

beepr::beep(4)
```


