---
title: "Episiotomy rates, 2016-2018"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

By **Christian McDonald**, Assistant Professor of Practice\
School of Journalism, Moody College of Communication\
University of Texas at Austin

This analysis looks at episiotomy rates using the [Texas Health Care Information Collection's Texas Inpatient Public Use Data File](https://www.dshs.texas.gov/thcic/hospitals/Inpatientpudf.shtm). The definition to calculate the rates comes from the [2019 Leapfrog Hospital Survey p103](https://www.leapfroggroup.org/sites/default/files/Files/2019HospitalSurvey_20190529_v8.0%20%28version%203%29.pdf).

> To start this analysis, I've used data filtered for AHRQ's definition for [uncomplicated deliveries](https://www.qualityindicators.ahrq.gov/Downloads/Modules/IQI/V2019/TechSpecs/IQI_33_Primary_Cesarean_Delivery_Rate_Uncomplicated.pdf), then identified and filtered for the vaginal deliveries based on Leapfrog's definition. At a future date, I'll use Leapfrog's definition against the original data and then compare.

The episiotomy definition uses several lists of ICD-10 codes. Those codes are processed into dataframes in the 01-process-lists notebook so they can be pulled into this and other notebooks.

## Setup and import

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
library(DT)
```

```{r imports}
### production data
del <- read_rds("data-processed/ahrq_del_ucmp.rds")

### testing data
# del <- read_rds("data-test/ahrq_del_ucmp_loop_test.rds")

### single quarter unfiltered for testing
# del <- read_tsv("data-raw/PUDF 1Q2018 tab-delimited/PUDF_base1_1q2018_tab.txt")

del %>% nrow()
```

## Setting up the denominator

Total number of vaginal deliveries during the reporting time period, with Excluded Populations removed.

### Filter for vaginal deliveries

The definition lists a number of `MS_DRG` and `APR_DRG` codes  that make up vaginal deliveries. The lists are defined in 01-process-lists and we pull them in here.

```{r lists_vag}
vag_msdrg_list <- read_rds("procedures-lists/lf_vag_msdrg.rds") %>% .$vag_msdrg
vag_msdrg_list
vag_aprdrg_list <- read_rds("procedures-lists/lf_vag_aprdrg.rds") %>% .$vag_aprdrg
vag_aprdrg_list
```

Filter our imported data for vaginal deliveries. Because we have two lists to consider, we'll create a column in our data where the values match, then filter them out.

```{r col_vag}
del <- del %>% 
  mutate(
    VAG = case_when(
      MS_DRG %in% vag_msdrg_list ~ TRUE,
      APR_DRG %in% vag_aprdrg_list ~ TRUE,
      TRUE ~ FALSE
    )
  )

# peek before filtering
del %>% 
  count(VAG)

# filter for vaginal deliveries only
del_vag <- del %>% 
  filter(VAG == T)
```

### Filter for exclusions

The next step is to: Exclude any cases with the following ICD-10-CM diagnostic code in a primary or secondary field:

- O66.0: Obstructed labor due to shoulder dystocia

We have to bring in our list of diagnostic columns and then filter based on the exception code. There is only one code `O660`, but we'll bring in from our processed lists anyway.

```{r filter_vag}
# import needed lists
diag_cols <- read_rds("procedures-lists/cols_diag.rds") %>% .$diag
vag_excl_list <- read_rds("procedures-lists/lf_vag_excl.rds") %>% .$vag_excl
vag_excl_list

# filter multiple columns for the list. keep the remainder.
del_vag_ex <- del_vag %>% 
  filter_at(
    vars(diag_cols),
    all_vars(
      !(. %in% vag_excl_list)
    )
  ) 

del_vag_ex %>% nrow()
```

### Set the episiotomy cases

This creates a column for cases where episiotomy is true. We have to look through each of the surgical procedure columns to check for the code.

> I'd like to refactor this method, but at least it is easy to see and understand.

```{r epi_col}
# list of codes for episiotmy, which is really one: 0W8NXZZ
epi_list <- read_rds("procedures-lists/lf_epi.rds") %>% .$epi
epi_list

del_epi <- del_vag_ex %>% 
  mutate(
    EPI = case_when(
      PRINC_SURG_PROC_CODE %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_1 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_2 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_3 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_4 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_5 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_6 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_7 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_8 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_9 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_10 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_11 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_12 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_13 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_14 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_15 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_16 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_17 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_18 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_19 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_20 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_21 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_22 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_23 %in% epi_list ~ TRUE,
      OTH_SURG_PROC_CODE_24 %in% epi_list ~ TRUE,
      TRUE ~ FALSE
    )
  )

```

## Statewide episiotomy rate, 2016-2018

We combine all three years of data to compare the percentage of episiotomy cases. The **TRUE** value is the percentage of cases where an episiotomy is performed.

```{r rate_state}
del_epi %>% 
  tabyl(EPI) %>% 
  rename(count = n) %>% 
  adorn_pct_formatting()
```

## Episiotomy rate for Laredo hospitals

```{r rate_laredo}
# filter for laredo hospitals

del_epi_lar <- del_epi %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))

del_epi_lar %>% 
  tabyl(PROVIDER_NAME, EPI) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()
```

### Episiotomy rates by hospital, by year

A look at the episiotomy rates for hospitals by year. We create the rate using the EPI column we created above, then pivot to do the math. We pivot again to see the years nicely in a table.

```{r by_year}
# pivot to crate the rate based on logical EPI column
del_epi_yr_data <- del_epi %>% 
  group_by(YR, PROVIDER_NAME, EPI) %>% 
  summarise(
    EPI_CNT = n()
  ) %>% 
  pivot_wider(names_from = EPI, values_from = EPI_CNT) %>% 
  rename(
    EPIF = "FALSE",
    EPIT = "TRUE"
  ) %>% 
  mutate(
    TOTAL = EPIF + EPIT,
    EPIRATE = round((EPIT / TOTAL) * 100,1)
  )

# peek at the results
del_epi_yr_data %>% head()

# select, pivot to see years.
del_epi_yr_table <- del_epi_yr_data %>% 
  filter(TOTAL >= 100) %>% 
  select(YR, PROVIDER_NAME, EPIRATE) %>% 
  pivot_wider(names_from = YR, values_from = EPIRATE) %>% 
  arrange(`2019` %>% desc())

del_epi_yr_table %>% head()

```

### Episiotomy rates by year, Laredo hospitals

The table above, filtered for Laredo.

```{r by_yr_laredo}
# filter for Laredo
del_epi_yr_table %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```

### Episiotomy rates by year, statewide and searchable


```{r datatable}
del_epi_yr_table %>% datatable()

```


## Write files

Writing out some data frames for use in other notebooks

```{r}
del_epi %>% write_rds("data-processed/epi.rds")

beepr::beep(4)
```


