---
title: "AHRQ Vaginal birth after Cesarean"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

By **Christian McDonald**, Assistant Professor of Practice\
School of Journalism, Moody College of Communication\
University of Texas at Austin

This is an analysis of the Vaginal Birth After Cesareans, as defined by [IQI 22 Vaginal Birth After Cesarean (VBAC) Delivery Rate, Uncomplicated](https://www.qualityindicators.ahrq.gov/Downloads/Modules/IQI/V2020/TechSpecs/IQI_22_Vaginal_Birth_After_Cesarean_(VBAC)_Delivery_Rate_Uncomplicated.pdf) in 2020.

## Definition

### Numerator

Number of vaginal deliveries among cases meeting the inclusion and exclusion rules for the
denominator. Vaginal deliveries are identified by any-listed ICD-10-PCS procedure code for vaginal delivery (VAGDELP* ).

### Denominator

Discharges with an ICD-10-CM diagnosis code for birth delivery outcome (DELOCMD) with any listed ICD-10-CM diagnosis codes for previous Cesarean delivery (PRVBACD).

Exclude cases:

- with any-listed ICD-10-CM diagnosis codes for abnormal presentation, fetal death, or multiple
gestation (Appendix A: PRCSECD )
- with an ungroupable DRG (DRG=999)
- with missing gender (SEX=missing), age (AGE=missing), quarter (DQTR=missing), year
(YEAR=missing) or principal diagnosis (DX1=missing)

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
library(DT)
library(tigris)

# suppresses grouping warning
options(dplyr.summarise.inform = FALSE)
```

## Import of deliveries

I start here with "All deliveries, identified by any-listed ICD-10-CM diagnosis code for outcome of delivery (DELOCMD)". This was processed in `01-process-loop`.

```{r imports}
# set test flag to FALSE to run production data
test_flag <- F

### test data
path_test <- "data-test/ahrq_del_all_loop_test.rds"

### production data
path_prod <- "data-processed/ahrq_del_cleaned.rds"

### import based on flag
if (test_flag == T) del <- read_rds(path_test) else del <- read_rds(path_prod)

del %>% nrow()
```

## Set up various processing lists

These are lists from the IQI 22 reference used for filtering and such. See 01-process-lists for definitions.

```{r lists}
# diagnostic columns
diag_cols <- read_rds("procedures-lists/cols_diag.rds") %>% .$diag

# surgical procedure columns
surg_cols <- read_rds("procedures-lists/cols_surg.rds") %>% .$surg

# appendix a complications list
prcsecd_list <- read_rds("procedures-lists/ahrq_prcsecd.rds") %>% .$prcsecd

# Previous Cesarean delivery diagnosis codes: (PRVBACD)
prvbacd_list <- read_rds("procedures-lists/ahrq_prvbacd.rds") %>% .$prvbacd

# Vaginal deliveries (VAGDELP)
vagdelp_list <- read_rds("procedures-lists/ahrq_vagdelp.rds") %>% .$vagdelp
```

## Filter deliveries to set denominator

### Filter out complicated deliveries

Start by filtering out rows "with any-listed ICD-10-CM diagnosis codes for abnormal presentation, preterm, fetal death, or multiple gestation (Appendix A: PRCSECD)".


```{r prcsecd}
del_ucmp <- del %>% 
  filter_at(
    vars(all_of(diag_cols)),
    all_vars(
      !(. %in% prcsecd_list)
    )
  )

del_ucmp %>% nrow()
```

### Filter out ungroupable DRG (DRG=999)

There are two Diagnosis Related Groups in the data, `MS_DRG`: Centers for Medicare and Medicaid Services (CMS) Diagnosis Related Group (DRG), as assigned for hospital payment for Medicare beneficiaries; and `APR_DRG`: All Patient Refined (APR) Diagnosis Related Group (DRG) as assigned by 3M APR-DRG Grouper). I filter out records with "999" in either of them.

```{r drg_ungroupable}
del_ucmp <- del_ucmp %>% 
  filter(
    (APR_DRG != "999"),
    (MS_DRG != "999")
  )

del_ucmp %>% nrow()
```

### Filter to keep only previous Cesarean delivery (PRVBACD).

```{r prvbacd}
del_denom <- del_ucmp %>% 
  filter_at(
    vars(all_of(diag_cols)),
    any_vars(
      . %in% prvbacd_list
    )
  )

del_denom %>% nrow()
```

This completes our "denominator" set of data. This is saved in `del_ucmp`.

## Numerator updates

Number of vaginal deliveries among cases meeting the inclusion and exclusion rules for the denominator. Vaginal deliveries are identified by any-listed ICD-10-PCS procedure code for vaginal delivery (VAGDELP).

We'll add a new column `VAGDELP` based on the codes. If the code is present, the value is `TRUE`.

```{r vagdelp}
ahrq_vbac <- del_denom %>% 
  mutate(
    VBAC = case_when(
      PRINC_SURG_PROC_CODE %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_1 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_2 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_3 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_4 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_5 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_6 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_7 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_8 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_9 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_10 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_11 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_12 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_13 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_14 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_15 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_16 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_17 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_18 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_19 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_20 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_21 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_22 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_23 %in% vagdelp_list ~ TRUE,
      OTH_SURG_PROC_CODE_24 %in% vagdelp_list ~ TRUE,
      TRUE                     ~  FALSE
    )
  )

ahrq_vbac %>% nrow()
```

This completes the processing of the data. `ahrq_vbac` is our working dataframe.

---

## VBAC analysis

- Do hospitals perform them?
- How many performed in 2019?

### Across data

```{r}
ahrq_vbac %>% 
  tabyl(VBAC) %>% 
  rename(count = n) %>% 
  adorn_pct_formatting()
```

### VBAC by hospital by year

This data is filtered for hospitals that have 30+ deliveries of patients with previous ceseareans in a given year.

```{r ahrq_vbac_rate_hosp_yr}
ahrq_vbac_rate_hosp_yr <- ahrq_vbac %>% 
  group_by(YR, THCIC_ID, PROVIDER_NAME) %>% 
  count(VBAC) %>% 
  # pivot to get rate for vbac
  pivot_wider(names_from = VBAC, values_from = n) %>% 
  rename(
    NVBAC = `FALSE`,
    YVBAC = `TRUE`
  ) %>% 
  mutate(
    PCTOT = NVBAC + YVBAC,
    VBAC_RATE = ((YVBAC / PCTOT) * 100) %>% round_half_up(1)
  ) %>% 
  filter(PCTOT >= 30 ) %>% 
  arrange(YR, PROVIDER_NAME)
  
ahrq_vbac_rate_hosp_yr %>% datatable()
```

### Rates in a table by year

```{r vbac_hosp_yr_table}
vbac_hosp_yr_table <- ahrq_vbac_rate_hosp_yr %>%
  select(YR, THCIC_ID, PROVIDER_NAME, VBAC_RATE) %>% 
  pivot_wider(names_from = YR, values_from = c(VBAC_RATE)) %>% 
  arrange(PROVIDER_NAME)

vbac_hosp_yr_table %>% datatable()
```

## VBACs by Laredo hospitals

```{r}
vbac_hosp_yr_table %>% 
  filter(str_detect(PROVIDER_NAME, "Laredo"))
```
## Summaries

### Statewide VBAC percentage across data

```{r ahrq_vbac_rate_tx}
ahrq_vbac %>% 
  tabyl(VBAC) %>% 
  rename(count = n) %>% 
  adorn_pct_formatting()
```

```{r ahrq_vbac_rate_tx_summary}
ahrq_vbac_rate_tx_summary <- ahrq_vbac %>% 
  group_by(VBAC) %>% 
  summarize(CNT = n()) %>% 
  pivot_wider(names_from = VBAC, values_from = CNT) %>% 
  rename(
    NVBAC_CNT = "FALSE",
    VBAC_CNT = "TRUE"
  ) %>% 
  mutate(
    TOTAL = NVBAC_CNT + VBAC_CNT
  ) %>% 
  mutate(
   SUMMARY = "TX",
   CATEGORY = "VAGINAL_BIRTH_AFTER_CESAREAN",
   MEASUREMENT = "RATE",
   VALUE = round_half_up((VBAC_CNT / TOTAL) * 100,1) # RATE
  ) %>%
  select(SUMMARY, CATEGORY, MEASUREMENT, VALUE)

ahrq_vbac_rate_tx_summary
```

### VBAC rate statewide by year

Excludes hospitals with fewer than 30 deliveries a year.

```{r ahrq_vbac_rate_tx_yr_summary}
ahrq_vbac_rate_tx_yr_summary <- ahrq_vbac %>% 
  group_by(VBAC, YR) %>% 
  summarize(CNT = n()) %>% 
  pivot_wider(names_from = VBAC, values_from = CNT) %>% 
  rename(
    NVBAC_CNT = "FALSE",
    VBAC_CNT = "TRUE"
  ) %>% 
  mutate(
    TOTAL = NVBAC_CNT + VBAC_CNT
  ) %>% 
  filter(TOTAL >= 30) %>% 
  mutate(
   SUMMARY = "TX",
   CATEGORY = "VAGINAL_BIRTH_AFTER_CESAREAN",
   MEASUREMENT = "RATE",
   VALUE = round_half_up((VBAC_CNT / TOTAL) * 100,1) # RATE
  ) %>%
  select(YR, SUMMARY, CATEGORY, MEASUREMENT, VALUE)

ahrq_vbac_rate_tx_yr_summary
```

### VBAC rate by hospital: Averaged, by year

```{r ahrq_vbac_rate_hosp_yr_summary}
ahrq_vbac_rate_hosp_yr_summary <- ahrq_vbac_rate_hosp_yr %>%
  ungroup() %>% 
  group_by(YR) %>% 
  summarize(
    SUMMARY = "HOSPITAL",
    CATEGORY = "VAGINAL_BIRTH_AFTER_CESAREAN",
    MEASUREMENT = "MEAN_OF_RATE",
    # MEDIAN = median(PCRATE),
    VALUE = round_half_up(mean(VBAC_RATE),1) #MEAN
  )

ahrq_vbac_rate_hosp_yr_summary
```

## Exports

Writing out some summary data, including:

- ahrq_vbac_rate_tx_yr_summary
- ahrq_vbac_rate_hosp_yr_summary

```{r exports}
if (test_flag == F) ahrq_vbac_rate_tx_yr_summary %>%
  write_rds("data-processed/ahrq_vbac_rate_tx_yr_summary.rds")

if (test_flag == F) ahrq_vbac_rate_hosp_yr_summary %>%
  write_rds("data-processed/ahrq_vbac_rate_hosp_yr_summary.rds")
```


## Closing

```{r end}
beepr::beep(4)
```



