---
title: "Summary statistics, 2016-3q2019"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

By **Christian McDonald**, Assistant Professor of Practice\
School of Journalism, Moody College of Communication\
University of Texas at Austin

## Purpose of the notebook

Each of the other analysis notebooks in the project export two types of summaries for each measure: statewide rates and averages of hospital rates. This notebook simply brings them all together into a single data file for export.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(fs)
library(tidyverse)
```

## Imports

```{r imports}
# set up folder
data_dir <- "data-processed"
# find the files
summary_files <- dir_ls(data_dir, recurse = TRUE, regexp = "_summary")
# peek at them
summary_files

# read and combine
summary_data <- summary_files %>%
  map_dfr(read_rds) %>% 
  arrange(SUMMARY, CATEGORY, YR)

# finished data
summary_data
```

## Exports

```{r write}
summary_data %>% 
  write_csv("exports/summary_data.csv")
```

