---
title: "A look at delayed records"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

By **Christian McDonald**, Assistant Professor of Practice\
School of Journalism, Moody College of Communication\
University of Texas at Austin

---

I want to see what percentage of records in the first quarter of a year are from the previous year. This uses a copy of the ahrq test file.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(fs)
library(tidyverse)
library(janitor)
```

## Set up import

We search through the `data` folder to build a list files to import into this notebook. The test data was created using the first 10,000 rows from one quarter of four years, 2016-2019.

```{r dirs_test}
data_dir <- "data-raw"
tsv_files <- dir_ls(data_dir, recurse = TRUE, regexp = "PUDF_base1_1q2019")

tsv_files
```

## Import the base1 files

At this time, our analysis utilizes only one (PUDF_base1) of several files in the release for each quarter.

Of note:

- There is a trailing tab on each row, whic brings in an unnecssary column. This is removed with `col_skip()`. The `EMERGENCY_DEPT_FLAG` col was introduced in 2017, so we have to remove two differnet "last columns".
- We set default type as col_character because some cols will appear as logical. We reset necessary cols as numbers where necessary.

```{r import, echo=T, results='hide', message=F, warning=F}
# warnings are suppressed, so check problems()
# add/remove test_ as necessary
base1 <- tsv_files %>%
  map_dfr(
    read_tsv,
    col_types = cols(
      .default = col_character(),
      X168 = col_skip(),
      X167 = col_skip()
    )
  ) %>%
  mutate_at(
    vars(contains("_CHARGES")), as.numeric
  )

# number of rows
base1 %>% nrow()

# klaxon for import complete
# beepr::beep(3)
```

## Filtering for deliveries

### Filtering muliple columns, multiple conditions

The logic here looks through a number of columns for a number of ICD codes.

In ths case, we are looking at all columns with "DIAG" in name for values in the `delocmd_list`, which comes from "DELOCMD*" in our IQI 33 reference. See `01-process-lists` for details.

Then we import the DELOCMD list and filter for it.

```{r deliveries}
delocmd_list <- read_rds("procedures-lists/ahrq_delocmd.rds") %>% .$delocmd

del <- base1 %>% 
  filter_at(
    vars(
      matches("_DIAG"),
      -starts_with("POA")
    ),
    any_vars(
      . %in% delocmd_list
    )
  )

del %>% nrow()
```

We peek here at the resulting frame to eyeball codes.

```{r peek_del}
del %>% 
  select(
    matches("_DIAG"),
    -starts_with("POA")
  ) %>% head(10)

```

## Exclusions from the deliveries

Some further notebooks need to exclude cases for complications like for abnormal presentation, fetal death, or multiple gestation. Those will be handled in those notebooks as needed.

Here we only filter out missing or bad data.

### Filter out blank cells per Appendix A

"with missing gender (SEX=missing), age (AGE=missing), quarter (DQTR=missing), year (YEAR=missing) or principal diagnosis (DX1=missing)."

In base1, the fields are `SEX_CODE`, `PAT_AGE`, `DISCHARGE` for both quarter and year, and `PRINC_DIAG_CODE`.

```{r clean}

del_cln <- del %>% 
  filter(
    SEX_CODE == "F",
    PAT_AGE != "`",
    RACE != "`",
    !is.na(DISCHARGE),
    !is.na(PRINC_DIAG_CODE)
  )

del_cln %>% nrow()
```

### Child-bearing age

Researchers at the Office of Health Affairs-Population Health, The University of Texas System work with the THCIC file daily and they suggest to filter deliveries to women of normal child-bearing age.

We'll look here how those ages break down in the cleaned file:

```{r peek_age}
del_cln %>% 
  count(PAT_AGE)
```

The codes for the ages 15-49 include 05-12. For HIV or drug patients it includes 23 (18-44 yrs). I import those from `procedures-lists`.

Here we will filter for those values.

```{r age}
age_list <- read_rds("procedures-lists/utoha_age.rds") %>% .$age

del_cln_age <- del_cln %>% 
  filter(PAT_AGE %in% age_list)

del_cln_age %>% nrow()
```

Peeking at records outside the child-bearing age list to make sure are none.

```{r age_test}
# set up not in
`%ni%` <- Negate(`%in%`)

del_cln_age %>% 
  filter(PAT_AGE %ni% age_list) %>% 
  select(PAT_AGE) %>% 
  count(PAT_AGE)
```

## Add convenience columns for dates

```{r add_yr}
del_cln_age_yr <- del_cln_age %>% 
  mutate(
    YR = substr(DISCHARGE, 1, 4)
  )
```

## Remove other years

Because of a reporting lag, there are years in the original data that we are not using for our analysis. At some point in 2015 there was a switch from ICD-9 to ICD-10 coding, so going eariler would require some conversions. Not impossible, but not in scope at this time to ease complication.

We are using full years from 2016-2018 and a partial year 2019 through the 2nd quarter release. This is subject to change as new data is released.

```{r filter_yr}
del_cln_age_yr <- del_cln_age_yr %>% 
  filter(YR %in% c("2015", "2016", "2017", "2018", "2019"))
```

## How many are from a previous year

```{r}
del_cln_age_yr %>% 
  tabyl(YR) %>% 
  adorn_pct_formatting()


```


